Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-28 latex/afm-cs-main.tex
Adjust RDI definition.
Update on Overleaf.

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}\\
  I & = \{k : r_{Z,k} = r_{z,s}\}
\end{align}
accumulates the deflection signal while scanning as a measure of the net force applied to the specimen  over time.

@@

% \SSData{G2}$& $g_6 = \SSData{G6}
The CS scans were reconstructed with BPVV. We set
${\alpha=\scanD{alph}}$ and ${\beta=\scanD{alpv}}$. For the
raster scans, we discard data from the re-trace and divided the
remaining data for each scan line into 512 bins based on the \xc
sensor measurements. We then average the data in each bin to obtain
the value of one pixel. To remove the affects of piezo creep and
sample tilt, we then de-trend each individual line. De-trending each
line causes the flat portion between the holes in the horizontal
direction to appear at a different height than the flat portion
between holes in the vertical direction. To remove this effect, we
select a column of pixels on the left and right side of each image
that does not cross any holes (i.e., a vertical line through the flat
area), and register each scan line to a common height along these columns.
This step eases comparison with the CS scans and was inspired by a
feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
color maps represent a range of $\pm$20 nm. The rows of pixels
indicated by the red lines are shown as cross sections in
Fig.~\ref{fig:pixel_rows}.

@@

\begin{figure}
  \includesvg[width=1\columnwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are
    included.}
  \label{fig:pixel_rows}
\end{figure}
For each raster scan and each CS scan, we computed the SSIM and PSNR
using the 1~Hz raster scan as the master and also computed the RDI
metric. These are plotted against total acquisition time in
Fig.~\ref{fig:time_vs_metrics}. Roughly speaking, image quality improves as
acquisition time increase. However, the metrics are quite noisy, leading to 
several inconsistencies. For example, it makes no sense that the 1~Hz, 25\% CS
scan has a \emph{worse} PSNR and SSIM than the 5~Hz, 25\% CS~scan;
nor does it make sense that the 8~Hz full raster scan has a worse SSIM and
PSNR than the 10~Hz full raster scan.

@@

Things are clearer if we plot the RDI for each scan against total
acquisition time, which is shown in Fig.~\ref{fig:time_damage}, and
this is where CS seems to shine. As one would expect, as imaging time
decreases, the RDI for each scan type increases. From
Fig.~\ref{fig:time_damage}, we see that for a fixed RDI, CS has a
faster imaging acquisition rate. The amount of improvement is best if
we need a very low RDI: for example, if we want to hold the RDI below~2, then we have to take the 1~Hz raster scan (512 seconds) while we
can achieve the same RDI via CS in about 42 seconds with the 12.5\%
sampling, which is a speed improvement of over a factor of 10. The higher of an
RDI we are willing to tolerate, the advantage of CS over raster
narrows. For example, the 8~Hz raster scan and 8~Hz, 12.5\% CS scan
have comparable RDIs, but now CS is only about 5 times faster. This is
a result of the constant overhead imposed by the engage/disengage and
$XY$-move states in CS which remains constant for different scan
rates.

\subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
Many sub-line sampling papers assume that the lines to sample are
selected randomly \cite{han_optimal_2018, Luo_nano_2015}. An even
simpler alternative to $\mu$-path sampling is to simply take a
standard raster scan with fewer lines. This is the technique we
consider in this subsection, by scanning images with 128 and 64 lines.
For each of these scenarios, we first divide the data for each line
into 512 bins. This gives an image that is 128 (resp., 64) pixels by
512 pixels. We then linearly interpolate along each column to produce
a 512 by 512 pixel image. Again, we take these coarser raster scans at
1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting images are shown in
Fig.~\ref{fig:results_subline_images}.

@@

Note the defect on the hole located in the second column, sixth row
from the top (of the grating holes). The CS-scans do a poor job
detecting this, while both coarse raster scans do so. However, the
other artifacts in the 64 line scan obscure the defect.

Fig.~\ref{fig:improve_512} compares the amount of speed improvement of
the different sub-sampling schemes over a full raster scan with 512
lines as a function of scan rate. As far as pure speed goes, the CS
scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
raster scan is close. At the same time, the image quality of the 1~Hz,
12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
However, this advantage quickly evaporates for faster scan rates.
Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
not only faster than the 12.5\% CS scan, it also has (arguably) better
image quality.

>>>>

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}\\
  I & = \{k : r_{Z,k} = r_{z,s}\} \nonumber
\end{align}
accumulates the deflection signal while scanning as a measure of the net force applied to the specimen  over time.

@@

% \SSData{G2}$& $g_6 = \SSData{G6}
The CS scans were reconstructed with BPVV. We set
${\alpha=\scanD{alph}}$ and ${\beta=\scanD{alpv}}$. For the
raster scans, we discard data from the re-trace and divided the
remaining data for each scan line into 512 bins based on the \xc
sensor measurements. We then average the data in each bin to obtain
the value of one pixel. To remove the effects of piezo creep and
sample tilt, we de-trend each individual line. De-trending each
line causes the flat portion between the holes in the horizontal
direction to appear at a different height than the flat portion
between holes in the vertical direction. To remove this effect, we
select a column of pixels on the left and right side of each image
that does not cross any holes (i.e., a vertical line through the flat
area), and register each scan line to a common height along these columns.
This step eases comparison with the CS scans and was inspired by a
feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
color maps represent a range of $\pm$20 nm. The rows of pixels
indicated by the red lines are shown as cross sections in
Fig.~\ref{fig:pixel_rows}.

@@

\begin{figure}
  \includesvg[width=1\columnwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are
    included.}
  \label{fig:pixel_rows}
\end{figure}
For each raster scan and each CS scan, we computed the SSIM and PSNR
using the 1~Hz raster scan as the master and also computed the RDI
metric. These are plotted against total acquisition time in
Fig.~\ref{fig:time_vs_metrics}. Roughly speaking, image quality improves as
acquisition time increase. However, the metrics are quite noisy and the results of the different methods are overlapping, making it difficult to extract a general result on the scanning approaches.

%leading to several inconsistencies. For example, it makes no sense that the 1~Hz, 25\% CS scan has a \emph{worse} PSNR and SSIM than the 5~Hz, 25\% CS~scan; nor does it make sense that the 8~Hz full raster scan has a worse SSIM and PSNR than the 10~Hz full raster scan.

@@

Things are clearer if we plot the RDI for each scan against total
acquisition time, shown in Fig.~\ref{fig:time_damage}.
%, and this is where CS seems to shine. 
As one would expect, as imaging time
decreases, the RDI for each scan type increases. Note that the CS curves are always better than that of the full raster scan. From
Fig.~\ref{fig:time_damage}, we see that for a fixed RDI, CS has a
faster imaging acquisition rate. The amount of improvement is best if
we need a very low RDI: for example, if we want to hold the RDI below~2, then we have to take the 1~Hz raster scan (512 seconds) while we
can achieve the same RDI via CS in about 42 seconds with the 12.5\%
sampling, which is a speed improvement of over a factor of 10. The higher of an
RDI we are willing to tolerate, the advantage of CS over raster
narrows. For example, the 8~Hz raster scan and 8~Hz, 12.5\% CS scan
have comparable RDIs, but now CS is only about 5 times faster. This is
a result of the constant overhead imposed by the engage/disengage and
$XY$-move states in CS which remains constant for different scan
rates.

\subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
Many sub-line sampling papers assume that the lines to sample are
selected randomly \cite{han_optimal_2018, Luo_nano_2015}. An even
simpler alternative to $\mu$-path sampling is simply to take a
standard raster scan with fewer lines. This is the technique we
consider in this subsection, by scanning images with 128 and 64 lines.
For each of these scenarios, we first divide the data for each line
into 512 bins. This gives an image that is 128 (resp., 64) pixels by
512 pixels. We then linearly interpolate along each column to produce
a 512 by 512 pixel image. Again, we take these coarser raster scans at
1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting images are shown in
Fig.~\ref{fig:results_subline_images}.

@@

Note the defect on the hole located in the second column, sixth row
from the top (of the grating holes). The CS-scans do a poor job
detecting this, while both coarse raster scans do so. However, the
other artifacts in the 64 line scan obscure the defect. It is important to note, however, that the appearance (or lack thereof) of such small features in the image is in large part a random occurrence. In our scans, the line scanner happened to pass through this region and capture the appropriate data while the $\mu$-path pattern used did not.

Fig.~\ref{fig:improve_512} compares the amount of speed improvement of
the different sub-sampling schemes over a full raster scan with 512
lines as a function of scan rate. As far as pure speed goes, the CS
scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
raster scan is close. At the same time, the image quality of the 1~Hz,
12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
However, this advantage quickly evaporates for faster scan rates.
Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
not only faster than the 12.5\% CS scan, it also has (arguably) better
image quality, at least on the sample used.
